%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                       %
%    C U R R I C U L U M    V I T A E   %
%                                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%--------------------------------------------------

\documentclass{scrartcl}

% Move the margin to the left of the page
\reversemarginpar

% New command defining the margin text style
\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}}

% Use the classicthesis style for the style of the document
\usepackage[nochapters]{classicthesis}

% Use the currvita style for the layout of the document
\usepackage[LabelsAligned]{currvita}

% Required for margin settings
\usepackage[marginparwidth=95pt]{geometry}

% Font color of your name at the top
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}

% Required for adding links and customizing them
\usepackage{hyperref}

% Set link colours
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon}

% Set the width of the date box in each block
\newlength{\datebox}\settowidth{\datebox}{MM-MM YYYY}

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

% Page Margins
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=50mm,
 right=20mm,
 top=15mm,
 bottom=15mm,
 }

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------
%       NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------

\begin{cv}{\spacedallcaps{Dr Grisha Szep}}\vspace{1.5em}
	% Your name
	
	\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em}
	% Personal information heading
	
	\NewEntry{website}{\href{https://gszep.com}{gszep.com}}
	% Birthplace and date
	
	\NewEntry{email}{\href{mailto:grisha.szep@gmail.com}{grisha.szep@gmail.com}}
	% Email address
	
	\NewEntry{phone}{ +44 7956 329010}
	
	\vspace{1em} % Extra space between major sections
	
	\noindent\spacedlowsmallcaps{Summary}\vspace{1em}
	
	\noindent \hspace{-6em} Researcher with 10+ years of experience within biomedical and computational academic 
	
	\noindent \hspace{-6em} research groups and software industry. Expertise in geometric deep learning, differential 
	
	\noindent \hspace{-6em} equations, signal processing and performance optimisation for big data problems. Creative 
	
	\noindent \hspace{-6em} and passionate about building visually stunning tools for solving complex problems.
	\vspace{2em}
	%------------------------------------------------------
	%                  WORK EXPERIENCE
	%------------------------------------------------------
	
	\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}
	
	\NewEntry{06/2022 - 05/2024}{Senior Machine Learning Engineer, \textsc{Cambridge}}
	
	\Description{\MarginText{Synteny\\Biotechnology}Third employee at a biotechnology start-up that harnesses the adaptive immune system. Built MLOps with emphasis on prototyping speed. Applied large language and diffusion models to design 3D protein structures. Quantisation for deployment on mobile devices. Rendered proteins in Blender. Workshop at NeurIPS and 2nd place in IMMREP23 competition.
		\newline
		Chief Research Officer: Neil \textsc{Dalchau}
		$\cdotp$ \href{mailto:neil@synteny.ai}{neil@synteny.ai}}
	
	
	\NewEntry{09/2017 - 09/2021}{Doctoral Researcher, \textsc{Cambridge}}
	
	\Description{\MarginText{Microsoft Research Cambridge}Member of biological programming research team. Thesis on geometric deep learning for point clouds and implicitly defined meshes with focus on high-dimensional single cell datasets. Developed applications in WebGL and D3. Published works in NeurIPS Proceedings, Natural Computing, Nature Comms and presented at JuliaCon.
		\newline
		Supervisor: Neil \textsc{Dalchau}
		$\cdotp$ \href{mailto:ndalchau@microsoft.com}{ndalchau@microsoft.com}}
	
	
	\NewEntry{11/2019 - 12/2020}{Senior Data Scientist, \textsc{London}}
	
	\Description{\MarginText{Flux}Delivering business intelligence and consumer analytics on receipt-level transaction data to merchant partners. Applied time series forecasting models in Scala, Python and PostgreSQL; built tools for A/B testing and actionable reports.
		\newline
		Chief Executive Officer: Matty \textsc{Cusdon-Ross}
		$\cdotp$  \href{mailto:matty@tryflux.com}{matty@tryflux.com}}
	
	\NewEntry{11/2016 - 11/2017}{Research Engineer, \textsc{Delft}}
	
	\Description{\MarginText{Birds.ai}Development and maintenance of drone image analysis pipeline for agricultural surveillance and industrial inspection. Applied computer vision and computational photography techniques for object detection and segmentation on high-resolution satellite imagery. Deployed web applications using AWS.
		\newline
		Chief Executive Officer: Camiel \textsc{Verschoor}
		$\cdotp$  \href{mailto:camiel@birds.ai}{camiel@birds.ai}}
	
	
	\NewEntry{09/2015 - 11/2016}{Graduate Researcher, \textsc{Vienna}}
	
	\Description{\MarginText{Institute of Science and Technology Austria}Investigation of non-equilibrium responses of the cytoskeleton and protein filament vortexes. Used Kinetic Monte-Carlo and ODEs to model polymerisation and applied computer vision and signal processing methods to extract sparse representations from fluorescence microscopy videos. Published works in Cell Press and Nature Physics.
		\newline
		Dr. Med. Michael \textsc{Sixt}
		$\cdotp$  \href{mailto:msixt@ist.ac.at}{msixt@ist.ac.at}
		Prof.~Karsten \textsc{Kruse}
		$\cdotp$ \href{mailto:k.kruse@physik.uni-saarland.de}{k.kruse@physik.uni-saarland.de}}
	
	\NewEntry{07/2014 - 09/2015}{Research Intern, \textsc{NASA Ames Silicon Valley}}
	
	\Description{\MarginText{NASA Ames\\Research Centre}Applying unsupervised signal processing methods to classify sleep stages on high resolution single channel electroencephalogram (EEG) recordings. Extraction of biomarkers related to neurophysiological disorders and development of human-machine interfaces.
		\newline
		Chief Executive Officer: Dr Philip \textsc{Low}
		$\cdotp$ \href{mailto:dhowe@neurovigil.com}{philip@neurovigil.com}}
	
	\pagebreak
	\NewEntry{06/2013 - 08/2013}{Research Studentship, \textsc{King's College
			London}}
	
	\Description{\MarginText{King's College London}Simulation of photon transport in random lasing process. Collection and analysis of data from optics experiments. Presentation of findings and evaluation as member of research team.
		\newline
		Research Supervisor: Dr Riccardo \textsc{Sapienza}
		$\cdotp$ \href{mailto:riccardo.sapienza@kcl.ac.uk}{riccardo.sapienza@kcl.ac.uk}}
	
	
	\NewEntry{Sep-Dec 2012}{Market Stall Owner, \textsc{Camden Market}}
	
	\Description{\MarginText{Camden Market}Managing market stall in tourist area of north London selling 3D IQ puzzles made of wood and bamboo. Creative presentation and sales to young and old audiences. Financial planning.
		\newline
		Supplier Contact: Ben \textsc{Meldrum}
		$\cdotp$ \href{mailto:ben@professorpuzzle.com}{ben@professorpuzzle.com}}
	
	
	%------------------------------------------------
	
	\vspace{1em} % Extra space between major sections
	
	%---------------------------------------------
	%       EDUCATION
	%---------------------------------------------
	
	\noindent\spacedlowsmallcaps{Education}\vspace{1em}
	
	%------------------------------------------------
	
	\NewEntry{09/2017 - 03/2022}{King's College London}
	
	\Description{\MarginText{Computational Biology \& Machine Learning}\textit{PhD}
		$\cdotp$ Randall Division of Cell \& Molecular Biophysics
		\newline 
		Published novel geometric deep learning algorithm for the inference of state-space structures in dynamical systems, with applications in developmental and synthetic biology. Writing software in Python and Julia in collaboration with Microsoft Research Cambridge. Published works in NeurIPS Proceedings, Natural Computing, Nature Comms and JuliaCon.
		\newline
		Attila \textsc{Csik\'asz-Nagy}
		$\cdotp$ \href{mailto:attila.csikasz-nagy@kcl.ac.uk}{attila.csikasz-nagy@kcl.ac.uk}
		Neil \textsc{Dalchau}
		$\cdotp$ \href{mailto:ndalchau@microsoft.com}{ndalchau@microsoft.com}}
	
	
	\NewEntry{09/2011 - 05/2015}{King's College London}
	
	\Description{\MarginText{Physics Masters}First Class
		$\cdotp$ \textit{Physics MSci}
		$\cdotp$ School of Natural \& Mathematical Science
		\newline 
		Focus on non-equilibrium statistical mechanics, information theory and complex networks. Masters project involved using the Keldysh formalism in quantum mechanics to investigate angular dependence of molecular current-voltage characteristics.
		\newline
		Project Supervisor: Prof.~Lev \textsc{Kantorovich}
		$\cdotp$ \href{mailto:lev.kantorovich@kcl.ac.uk}{lev.kantorovich@kcl.ac.uk}}
	
	%------------------------------------------------
	
	\NewEntry{08/2013 - 06/2014}{University of California, Berkeley}
	
	\Description{\MarginText{Exchange Year}GPA: 3.7
		$\cdotp$ \textit{Physics Major}
		$\cdotp$ College of Letters \& Science
		\newline
		Attended lectures at the Redwood Center for Theoretical Neuroscience. Expanded knowledge on analytical mechanics, special relativity, solid state physics and machine learning. Duration of stay motivated academic path towards machine learning.
		\newline
		Study Abroad Tutor: Nicola \textsc{Bonini}
		$\cdotp$ \href{mailto:nicola.bonini@kcl.ac.uk}{nicola.bonini@kcl.ac.uk}}
	
	%------------------------------------------------
	
	\vspace{1em} % Extra space between major sections
	
	%----------------------------------------------------------------------------------------
	%       COMPUTER SKILLS
	%----------------------------------------------------------------------------------------
	
	\spacedlowsmallcaps{Computer Skills}\vspace{1em}
	
	\Description{\MarginText{Intermediate}
		AWS, GCP, Next.js,
		C++, C\#, PostgreSQL, HLSL, NodeJs}
	
	
	\Description{\MarginText{Advanced}
		PyTorch, JAX, Julia, WebGL, Flux.jl, Latex, Git,
		Linux, DevOps, MLOps, D3.js}
	
	\Description{\MarginText{Datasets}
		Single-cell, 3D Protein Structure, Fluorescence Microscopy, Satellite Imagery
	}
	
	\vspace{1em} % Extra space between major sections
	
	%----------------------------------------------------------------------------------------
	%       PUBLICATIONS
	%----------------------------------------------------------------------------------------
	
	\spacedlowsmallcaps{Works}\vspace{1em}
	
	\Description{\MarginText{Published}Caballero-Mancebo, S. et al. 2024. Nature Physics.\\Friction forces determine cytoplasmic reorganization and shape changes of ascidian oocytes upon fertilization}
	\Description{Cornwall, L. \& Szep, G. et al. 2023. NeurIPS Generative AI \& Biology Workshop.\\Fine-tuned protein language models capture T cell receptor stochasticity.}
	\Description{Coppard, V. \& Szep, G. et al. 2023. bioRxiv, 2023.12. 21.572741\\FlowAtlas.jl : an interactive tool bridging FlowJo and computational tools in Julia.}
	\Description{Szep, G. 2022. Thesis. King's College London\\Inferring Bifurcations between Phenotypes.}
	\Description{Szep, G. et al. 2021. Advances in Neural Information Processing Systems\\Parameter Inference with Bifurcation Diagrams.}
	\Description{Peruzzo, M., Hassani, F. \& Szep, G. et al. 2021. Physical Review X: Quantum\\Geometric superinductance qubits.}
	\Description{Grant, P. \& Szep, G. et al. 2020. Nature Communications 11 (1), 1-8\\Interpretation of morphogen gradients by a synthetic bistable circuit.}
	\Description{Dalchau, N. \& Szep, G. et al. 2018. Natural computing 17 (4), 761-779\\Computing with biological switches and clocks.}
	\Description{M\"uller, J. \& Szep, G. et al. 2016. Cell 171 (1), 188-200. e16\\Load-adaptation of lamellipodial actin networks.}
	
	
	\Description{\MarginText{Conferences}FlowAtlas.jl : an interactive tool bridging FlowJo and computational tools in Julia.\\JuliaCon 2021. \url{youtu.be/FeYrFKgP91s}}
	\Description{Inference of Bifurcations with Differentiable Continuation.\\JuliaCon 2020. \url{youtu.be/vp-206RgeVE}}
	\Description{2019. Quantitative Systems Biology Workshop. London. Organisation Committee}
	\Description{2019. Bioinspired analysis of dynamical systems, Hungary. Talk}
	\Description{2018. EMBL Symposium: Biological Oscillators, Heidelberg. Poster}
	
	%------------------------------------------------
	
	\vspace{1em} % Extra space between major sections
	
	%----------------------------------------------------------------------------------------
	%       AWARDS & QUALIFICATIONS
	%----------------------------------------------------------------------------------------
	
	\spacedlowsmallcaps{Awards \& Qualifications}\vspace{1em}
	
	\Description{\MarginText{Awards}2018 $\cdotp$ Microsoft Research PhD Scholarship}
	
	\vspace{-0.5em}
	\Description{2014 $\cdotp$ Study Abroad Student Award -- King's College London}
	
	\vspace{-0.5em} % Negative vertical space to counteract the vertical space
	
	\Description{2013 $\cdotp$ The Gordon Rogers Scholarship - Top 5  Performing Students}
	
	\vspace{-0.5em} % Negative vertical space to counteract the vertical space
	
	\Description{2013 $\cdotp$ Andrewes Prize  - Best Examination Performance}
	
	\vspace{-0.5em} % Negative vertical space to counteract the vertical space
	
	\Description{2012 $\cdotp$ Dillon Prize  - Best Examination Performance}
	
	%------------------------------------------------
	
	\vspace{1em}
	
	\Description{\MarginText{Qualifications}2016
		$\cdotp$ Electron Microscope Training - Institute of Science \& Technology}
	
	\vspace{-0.5em}
	% Negative vertical space between every \Description command
	
	\Description{2013 $\cdotp$ Basic Laser Safety Certificate - King's College London}
	
	\vspace{-0.5em}
	% Negative vertical space between every \Description command
	
	\Description{2012 $\cdotp$ Kids Ski Instructor Certificate - Swiss Snowsports}
	
	
	%------------------------------------------------
	
\end{cv}

\end{document}
